\Large \includegraphics[height=\baselineskip]{title.png} \\ \vspace{0.65mm} \large \normalfont CSE 227: Computer Security - Spring 2017 \\ \textit{ University of California San Diego }

### 2017-06-12 docs/paper.tex
Expanding related work and fix a few syntax

Currently, most popular website will show the hostname in Unicode depends on the language setting to defend IDN attack.
For example, Chrome will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language.

@@

Many relevant studies have been conducted to show the vulnerability of IDN and provide possible solution to mitigate IDN homograph attack.
In 2001, Evgeniy Gabrilovich and Alex Gontmakher has proved the feasibility of such attack based on the vulnerability of unicode in \textit{The Homograph Attack}~\cite{theHomoAttack}.
In 2006, Vicktor Krammer proposed a defense mechanism based on address bar highlighting/indication technique and better UI of the browsers~\cite{phishdefenseKV}.
His method of defense mainly target at regular users who do not neccessarily have relevant knowledge and through the better rendering of address along with explicit notification or alert on phishing url users would be aware of malicious website.
Manurer and Höfer believed that safe guard based on browsers' blacklist is far from enough to protect users from sophisticated phishing attacks~\cite{proc-eds-2012}.
They proposed an advanced method based on url components and spell checking functionality of search engine.
In this method, an url would be divided into several components, namely, basename, subdomains, pathdomain, brandname.
Each of this components will be sent to search engine as a term for spelling check and in the cases that spelling suggestion is returned the url will be counted as suspicious.
The major browsers have their own IDN policies to defend against IDN homograph attack.
Google Chrome, starting with Chrome 51, will display punycode if certain tests fail on the input url.
These tests include but not limited to converting to unicode, less than one numbering systems involved, no invisible characters, etc.
IE displays urls in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
Firefox uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays unicode when url consists of any single script, any single script plus Latin, or it's in the whitelist of other combinations.
Opera shows IDN only for whitelisted TLDs.
Safari has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.

>>>>

Currently, most popular browsers will show the hostname in Unicode depends on the language setting to defend IDN attack.
For example, Google Chrome\footnote{\url{https://www.google.com/chrome}} will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language.

@@

Many relevant studies have been conducted to show the vulnerability of IDN and provide possible solution to mitigate IDN homograph attack.
In 2001, Evgeniy Gabrilovich and Alex Gontmakher has proved the feasibility of such attack based on the vulnerability of unicode in \textit{The Homograph Attack}~\cite{theHomoAttack}.
In 2006, Vicktor Krammer proposed a defense mechanism based on address bar highlighting/indication technique and better UI of the browsers~\cite{phishdefenseKV}.
His method of defense mainly target at regular users who do not neccessarily have relevant knowledge and through the better rendering of address along with explicit notification or alert on phishing url users would be aware of malicious website.
This method check each character in an url seperately, highlighting digits or characters of various scripts in different background color so that users will be aware of the difference.
It also suggest using larger font size in the address bar to help distinguish possible homograph characters from the Latin letter and alerting users when multiscript is detected by means of scripts block\footnote{\url{http://www.unicode.org/reports/tr24/}}.
His proposal was innovative in his year but not entirely accurate because characters from the same script may be in different blocks while characters from different scripts sometimes lie in the same block.
Manurer and Höfer believed that safe guard based on browsers' blacklist is far from enough to protect users from sophisticated phishing attacks~\cite{proc-eds-2012}.
They proposed an advanced method based on url components and spell checking functionality of search engine.
In this method, an url would be divided into several components, namely, basename, subdomains, pathdomain, brandname.
Each of this components will be sent to search engine as a term for spelling check and in the cases that spelling suggestion is returned the url will be counted as suspicious.

The major browsers have their own IDN policies to defend against IDN homograph attack.
Google Chrome, starting with Chrome 51, will display punycode if certain tests fail on the input url.
These tests include but not limited to converting to unicode, less than one numbering systems involved, no invisible characters, etc.
Internet Explorer\footnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays urls in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.
Firefox\footnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays unicode when url consists of any single script, any single script plus Latin, or it's in the whitelist of other combinations.
Opera\footnote{\url{http://www.opera.com}} shows IDN only for whitelisted TLDs.
Safari\footnote{\url{https://www.apple.com/safari}} has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.
